---
title: "FPCA and Functional Linear regression"
author: "GWW 12031299"
date: "2021/4/16"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
rm(list = ls())
library(fda)
library(ggplot2)
library(reshape2)
library(freqdom)
setwd("E://R Files/Functional Data Analysis")
load('Data Sets/fly.Rdata')
eggcount = medfly$eggcount
day = 1:26
```

# fPCA and dynamic fPCA
## Smooth the data under best basis function num 12 basis 
```{r}
# eggcountfdata = fdata(t(medfly$eggcount),names=list("day","eggcount")) # convert data to fdata 
# lifespan = medfly$lifetime
# nb = floor(seq(5,26,len=6))
# lam = 2^(-5:15)
# optbasis = optim.basis(eggcountfdata,lambda=lam,numbasis=nb,type.basis="bspline")
# basis_choice = data.frame(lam, t(optbasis$gcv))
# colnames(basis_choice) = c("lambda","numbasis1","numbasis2","numbasis3")
# png(file = "Basis_S.png")
# matplot(t(optbasis$gcv),type="l",main="GCV with bspline basis",xlab="num of bspline",ylab="GCV value") # verify the choose of num 12 basis
# dev.off()

bbasis_ = create.bspline.basis(c(0,26), nbasis = 12, norder=4) 
S_dayEggfd = with(medfly, smooth.basis(day,eggcount,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount"))$fd)
# with(medfly, plotfit.fd(eggcount,day,S_dayEggfd,ask=TRUE)) # a Functional Data Object With Data
png(file = "Smooth.png")
plot(S_dayEggfd,ylim=c(-20,120)) # the aligned original recordings of the force relative to a baseline value
dev.off()

S_eggcountpcaobj = pca.fd(fdobj=S_dayEggfd,nharm=4,fdPar(bbasis_))
S_eggcountpcaobj$varprop # 0.3745757 0.2957662 0.1685607 0.0437355
pcanum = c(1:8)
S_eigenvalues = S_eggcountpcaobj$values[1:8]
S_cum_eigenvalues = cumsum(S_eigenvalues)/sum(S_eigenvalues)

variation_S = ggplot(NULL,aes(pcanum,S_cum_eigenvalues))+geom_point(color = "darkred")+geom_line(linetype="dotted")+geom_hline(yintercept=0.9, linetype='dashed',size =1,col=2)+   theme_bw()+theme(panel.grid=element_blank())+xlab("No of component") +ylab("cumulative variance explained")
ggsave(variation_S,filename = "variationS.png",width = 8,height = 4)

S_harmfd = S_eggcountpcaobj$harmonics # new basis function given by PCA
S_harmvals = melt(data.frame(day,eval.fd(day,S_harmfd)),id="day") # PC values
colnames(S_harmvals) = c("day","PC","value")
pc_S = ggplot(S_harmvals,aes(day,value,group=PC,color=PC,shape=PC))+geom_line(linetype="dashed")+theme_bw()+theme(panel.grid=element_blank())+xlab("day")+ylab("PC value") # the first four principal component curves for data without regularization, there is substantial variability and a clear need for smoothing or regularizing of the estimated principal component curves
ggsave(pc_S,filename = "pcS.png",width = 8,height = 4)
```

## Roughness smooth the data first, then carry out an unsmoothed PCA
```{r}
bbasis = create.bspline.basis(rangeval=c(0,26), nbasis = 26, norder=4) 
D2fdPar = fdPar(bbasis,Lfdobj=int2Lfd(2),lambda=10) # best lambda is given by A1
P_dayEggfd = smooth.basis(day,eggcount,D2fdPar,
                        fdnames=list("Day", "lifespan", "eggcount"))$fd
png(file = "Roughness.png")
plot(P_dayEggfd) 
dev.off()

eggcountpcaobj = pca.fd(fdobj=P_dayEggfd,nharm=4, harmfdPar=D2fdPar)
pcanum = c(1:8)
eigenvalues = eggcountpcaobj$values[1:8]
cum_eigenvalues = cumsum(eigenvalues)/sum(eigenvalues)
setwd("E://R Files/Functional Data/Projects/A2")
write.table(eggcountpcaobj$scores[,1:4],"eggcount-pc4", col.names = c("PC1","PC2","PC3","PC4"))

variation_P = ggplot(NULL,aes(pcanum,cum_eigenvalues))+geom_point(color = "darkred")+geom_line(linetype="dotted")+geom_hline(yintercept=0.9, linetype='dashed',size =1,col=2)+
        theme_bw()+theme(panel.grid=element_blank())+xlab("No of component") +ylab("cumulative variance explained")
ggsave(variation_P,filename = "variationP.png",width = 8,height = 4)

harmfd = eggcountpcaobj$harmonics # new basis function given by PCA
harmvals = data.frame(day,eval.fd(day,harmfd)) # PC values
harmvals = melt(harmvals,id="day")
colnames(harmvals) = c("day","PC","value")
pc_P = ggplot(harmvals,aes(day,value,group=PC,color=PC,shape=PC))+geom_line(linetype="dashed")+theme_bw()+theme(panel.grid=element_blank())+xlab("day")+ylab("PC value")
ggsave(pc_P,filename = "pcP.png",width = 8,height = 4)

sharmvals = eval.fd(day,harmfd)%*%diag(sqrt(eggcountpcaobj$values[1:4]))
colnames(sharmvals) = c("PC1","PC2","PC3","PC4")
sharmvals = melt(data.frame(day,sharmvals),id="day")
colnames(sharmvals) = c("day","PC","value")
pc_P_c = ggplot(sharmvals,aes(day,value,group=PC,color=PC,shape=PC))+geom_line(linetype="dashed")+theme_bw()+theme(panel.grid=element_blank())+xlab("day")+ylab("PC value")
ggsave(pc_P_c,filename = "pcPcentered.png",width = 8,height = 4)
```

## Visualizing the results: plotting components as perturbations of the mean)
```{r warning=FALSE, fig.show="hide"}
plot.pca.fd(eggcountpcaobj, cex.main=0.9) # the effect on the overall mean curve of adding and subtracting a suitable multiple of each of the first four smoothed principal component curves

mean_ = eggcountpcaobj$meanfd$coefs
effects = matrix(0,26,4)
d = rep(0,4)
eigen_ = eval.fd(day,eggcountpcaobj$harmonics)
for (i in c(1:4)){
  d[i] = sqrt(eggcountpcaobj$values)[i]
  effects[,i] = 2*d[i]*eigen_[,i]
} # the variation in the functional data that is contributed by each eigenfunction
up_ = mean_+effects[,1]
lower_ = mean_-effects[,1]
perturbations = data.frame(day,mean_,up_,lower_)
perturbations = melt(perturbations,id="day")
colnames(perturbations) = c("day","PC","value")
effect_ = ggplot(perturbations,aes(day,value,group=PC,color=PC,shape=PC))+geom_line(linetype="dashed")+theme_bw()+theme(panel.grid=element_blank())+xlab("day")+ylab("PC value")# the effects on the mean curve
ggsave(effect_,filename = "effect.png",width = 8,height = 4)
eggcountvarmx = varmx.pca.fd(eggcountpcaobj) # Varimax rotation: find a more interpretable basis
plot(eggcountvarmx)
```

## Dynamic fPCA: DPCA decomposition outputs components which are uncorrelated in time
```{r}
X_eggcount = as.matrix(eggcount)
eggcountpca = prcomp(X_eggcount, center=TRUE,rank.=4)
summary(eggcountpca) # the explained variation is smaller than no roughness PCA

eggcountdpca = dpca(X_eggcount, q=5, Ndpc=4)
dvar_ = eggcountdpca$var
cat("var contribution from dpca output \n \t",dvar_[1:4])

dvariation = ggplot(NULL,aes(pcanum,cumsum(dvar_[1:8])))+geom_point(color = "darkred")+geom_line(linetype="dotted")+geom_hline(yintercept=0.9, linetype='dashed',size =1,col=2)+ theme_bw()+theme(panel.grid=element_blank())+xlab("No of component") +ylab("cumulative variance explained")
ggsave(dvariation,filename = "dvariation.png",width = 8,height = 4)
```

# Functional Linear Models (Scale-functional)
```{r}
R2 = function(y,y_hat,y_train_bar){
  R2 = 1-sum((y-y_hat)^2)/sum((y-y_train_bar)^2)
  return(R2)
}

osR2 = function(y_test,y_pre,y_train_bar){
  osR2 = 1-sum((y_test-y_pre)^2)/sum((y_test-y_train_bar)^2)
  return(osR2)
}

# flm_stdlist = function(y,y_hat,flm,xfd){
#   N = length(y)
#   resid = y - y_hat
#   SigmaE = sum(resid^2)/(N-flm$df)*diag(rep(1,N))
#   y2cMap = xfd$y2cMap
#   stderrList = fRegress.stderr(flm, y2cMap, SigmaE)
#   return(stderrList) # flm results and contain the beta_std, xfd is a smooth.basis that generates the dependent variable objects. 
# }

flm_stdlist = function(y,y_hat,flm,basisnum){
  N = length(y)
  resid = y - y_hat
  SigmaE = sum(resid^2)/(N-flm$df)*diag(rep(1,N))
  y2cMap = diag(N)
  stderrList = fRegress.stderr(flm, y2cMap, SigmaE)
  return(stderrList) # for scaled response variable
}

betaconfInter = function(beta_hat,beta_std,beta_num){
  betanum = c(1:beta_num) # coefficient beta num
  betaup = beta_hat+2*beta_std
  betalow = beta_hat-2*beta_std
  betaconf = data.frame(betanum,betaest,betaup,betalow)
  return(betaconf)
}
```

## Scalar-on-functional regression model
### Regression using restricted basis functions: No roughness lambda
```{r}
train_ind = 1:35
X_train = eggcount[,train_ind]
X_test = eggcount[,-train_ind]
bbasis_ = create.bspline.basis(c(0,26), nbasis=12, norder=4) # not full model, this result is given by A1
xfd = smooth.basis(day,X_train,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount")) # estimated value of x(t)
xfdobj_S = xfd$fd # this fob is relevent to the xfdlist name of flm_S

lifespan = as.numeric(medfly$lifetime[train_ind])
lifespan_bar = mean(lifespan)
y_test = as.numeric(medfly$lifetime[-train_ind])

flm_S = fRegress(lifespan~xfdobj_S) # model building in another way

lifespan_fit_S = flm_S$yhatfdobj
# Fitted_S = ggplot(NULL,aes(lifespan_fit_S,lifespan))+geom_point(color = "darkred")+geom_abline(slope=1)+theme_bw()+theme(panel.grid=element_blank())+xlab("True value") +ylab("Fitted value")
# ggsave(Fitted,filename = "Fitted_S.png",width = 8,height = 4)

R2_S = R2(lifespan,lifespan_fit_S,lifespan_bar)
print(paste("R2 =",R2_S)) # R2 = 0.992427274348569
RMSE_S = sqrt(mean((lifespan-lifespan_fit_S)^2))
print(paste("RMSE =",RMSE_S))

betaeststd = flm_stdlist(lifespan,lifespan_fit_S,flm_S,xfd) # to calculate the projection matrix: solve(t(Z)*Z+lambdaR0)t(Z)

X_testfd = smooth.basis(day,X_test,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount"))$fd
X_testfdobj = fRegress(y_test~X_testfd, method="model")$xfdlist$X_testfd

lifespan_pre_S = inprod(flm_S$betaestlist$xfdobj_S$fd, X_testfdobj) # matrix calculation to get prediction value
osR2_S = osR2(y_test,lifespan_pre_S,lifespan_bar)
print(paste("osR2 =",osR2_S)) # 0.980643976796598

betaestfd = betaeststd$betaestlist$xfdobj_S$fd

png(file = "Betafunc_S.png")
plot(betaestfd, xlab="Day", ylab="Weight function Beta", lwd=2, col=2,col="blue",ylim=c(-0.8,1.8))
betaestfd_std = betaeststd$betastderrlist[[2]]
lines(betaestfd+2*betaestfd_std, lty=2, lwd=2, col="blue") 
lines(betaestfd-2*betaestfd_std, lty=2, lwd=2, col="blue")
dev.off()

betaest = betaeststd$betaestlist$xfdobj_S$fd$coefs # coefficient function
# betaestfd = flm_S$betaestlist$xfdobj_S$fd
# all.equal(betaestfd1,betaestfd)
betaest_std = betaeststd$betastderrlist[[2]]$coefs # betahat_std
betaconf = betaconfInter(betaest,betaest_std,12) # confidence interval
colnames(betaconf) = c("num","betahat","up","low")
betaconf = melt(betaconf,id="num")
colnames(betaconf) = c("num","Beta","value")
Beta_S = ggplot(betaconf,aes(num,value,group=Beta,color=Beta,shape=Beta))+geom_line(linetype="dashed")+geom_hline(yintercept=0.0, linetype='dashed',size =1,col=2)+theme_bw()+theme(panel.grid=element_blank())+xlab("Betalist")+ylab("Lifetime Reg. Coeff.") # Regression function Beta for fruit flies' lifetime
ggsave(Beta_S,filename = "Beta_S.png",width = 8,height = 4)
```

### Choice of lambda
```{r, message=FALSE, warning=FALSE,include=FALSE}
# xfdlist = list(const=rep(1, 50), xfdobj=xfdobj) 
# betabasis_cons = create.constant.basis(c(0, 26))
# betafd_cons = fd(0, betabasis_cons)
# betafdPar_cons = fdPar(betafd_cons) 
# betafd_basis = create.bspline.basis(c(0,26), nbasis=26, norder=4)
# betafdPar_basis = fdPar(betafd_basis, Lfdobj=int2Lfd(2), lambda=10) 
# betalist = list(const=betafdPar_cons, basisfd=betafdPar_basis) 

bbasis_ = create.bspline.basis(c(0,26), nbasis=12, norder=4) 
X_train = eggcount[,1:35]
lifespan = as.numeric(medfly$lifetime[1:35])
xfdobj = smooth.basis(day,X_train,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount"))$fd 
xfdlist = list(const=rep(1, 35), xfdobj=xfdobj) 

betabasis_cons = create.constant.basis(c(0, 35))
betafd_cons = fd(1, betabasis_cons)
betafdPar_cons = fdPar(betafd_cons) 
betafd_basis = create.bspline.basis(c(0,26), nbasis=35, norder=4) 
betafdPar_basis = fdPar(betafd_basis, Lfdobj=int2Lfd(2), lambda=10) 
betalist = list(const=betafdPar_cons, basisfd=betafdPar_basis)

detach(package:fda)
library(fda,lib.loc="D:/R/R-4.0.2/library/fdaold")
loglam = seq(-0.1,3.9,0.01)
nlam = length(loglam)
SSE.CV = rep(0,nlam)
for (i in 1:nlam){
  lambda = 10^loglam[i]
  betalist$basisfd$lambda = lambda
  betalist_i = betalist
  flm_cv = fRegress.CV(lifespan, xfdlist, betalist_i)
  SSE.CV[i] = flm_cv$SSE.CV
}
save(SSE.CV, file = "CV.RData") # there are many variables
plot(loglam, SSE.CV/1000, type="b", xlab="log roughness parameter lambda", ylab="Cross−validation score CV(*10^3)")

CV = ggplot(NULL,aes(loglam,SSE.CV/1000))+geom_point(color = "darkred")+geom_abline(slope=1)+theme_bw()+theme(panel.grid=element_blank())+xlab("log_10 roughness parameter lambda") +ylab("Cross−validation score CV(*10^3)")
ggsave(CV,filename = "CV.png",width = 6,height = 4)
min(SSE.CV)

```

### Regularization with roughness penalties: Best lambda
```{r, message=FALSE, warning=FALSE}
detach(package:fda)
library(fda)
train_ind = 1:35
X_train = eggcount[,train_ind]
X_test = eggcount[,-train_ind]
lifespan = as.numeric(medfly$lifetime[train_ind])
lifespan_bar = mean(lifespan)
y_test = as.numeric(medfly$lifetime[-train_ind])

bbasis_ = create.bspline.basis(c(0,26), nbasis=12, norder=4) 
xfd = smooth.basis(day,X_train,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount")) 
xfdobj = xfd$fd
model = fRegress(lifespan~xfdobj, method="model")

lambda =  15074.36 # 22510
betabasis_bbasis = create.bspline.basis(rangeval=c(0,26), nbasis = 35, norder=4) 
betafd = fd(rep(1, 35), betabasis_bbasis) # betalistlist
betafdPar = fdPar(betafd, Lfdobj=int2Lfd(2), lambda=lambda) # roughness betalist
model$betalist$xfdobj = betafdPar # replace the betalist, i.e. the regress coefficient function beta(t)
flm_P = do.call('fRegress',model) 
lifespan_fit = flm_P$yhatfdobj
# Fitted = ggplot(NULL,aes(lifespan_fit,lifespan))+geom_point(color = "darkred")+geom_abline(slope=1)+theme_bw()+theme(panel.grid=element_blank())+xlab("True value") +ylab("Fitted value")
# ggsave(Fitted,filename = "Fitted.png",width = 8,height = 4)

R2_P = R2(lifespan,lifespan_fit,lifespan_bar)
print(paste("R2 =",R2_P)) # R2 = 0.987987921981976, smaller than no penalty
RMSE_P = sqrt(mean((lifespan-lifespan_fit)^2))
print(paste("RMSE =",RMSE_P))

X_testfd = smooth.basis(day,X_test,
        bbasis_, fdnames=list("Day", "lifespan", "eggcount"))$fd
X_testfdobj = fRegress(y_test~X_testfd, method="model")$xfdlist$X_testfd
lifespan_pre_P = inprod(flm_P$betaestlist$xfdobj$fd, X_testfdobj) # useage of predict
osR2_P = osR2(y_test,lifespan_pre_P,lifespan_bar)
print(paste("osR2 =",osR2_P)) # 0.976094642992361

betaeststd = flm_stdlist(lifespan,lifespan_fit,flm_P,35) # scaled response
# betaeststd = flm_stdlist(lifespan,lifespan_fit,flm_P,xfd) # functional response
betaestfd = betaeststd$betaestlist$xfdobj$fd
png(file = "Betafunc.png")
plot(betaestfd, xlab="Day", ylab="Weight function under roughness", lwd=2, col=2,col="blue",ylim=c(-0.8,1.8))
betaestfd_std = betaeststd$betastderrlist[[2]]
lines(betaestfd+2*betaestfd_std, lty=2, lwd=2, col="blue") 
lines(betaestfd-2*betaestfd_std, lty=2, lwd=2, col="blue")
dev.off()

betaest = betaeststd$betaestlist$xfdobj$fd$coefs 
betaest_std = betaeststd$betastderrlist[[2]]$coefs 
betaconf = betaconfInter(betaest,betaest_std,35)
colnames(betaconf) = c("num","betahat","upbound","lowbound")
betaconf = melt(betaconf,id="num")
colnames(betaconf) = c("num","RegCoeff","value")
Beta = ggplot(betaconf,aes(num,value,group=RegCoeff,color=RegCoeff,shape=RegCoeff))+geom_line(linetype="dashed")+geom_hline(yintercept=0.0, linetype='dashed',size =1,col=2)+theme(legend.position = c(0, 0),legend.justification = c(0, 1))+theme_bw()+theme(panel.grid=element_blank())+xlab("50 Bspline basis functions ")+ylab("Lifetime Reg. Coeff.") #lambda=22510
ggsave(Beta,filename = "Beta.png",width = 8,height = 4)
```

## Functional principal component regression
```{r}
eggcountpc=read.table("E://R Files/Functional Data/Projects/A2/eggcount-pc4",header = TRUE,row.names = 1)
pcscore = as.matrix(eggcountpc)[,1:3]
pclifespan = as.matrix(medfly$lifetime)
fpclm=lm(pclifespan~pcscore)
summary(fpclm)
R2_pca = R2(pclifespan,fpclm$fitted.values,lifespan_bar)
print(paste("R2 =",R2_pca)) # R2=0.969501679534734

fpcabeta = fpclm$coef[2]*eggcountpcaobj$D2fdPar[1]+
fpclm$coef[3]*eggcountpcaobj$D2fdPar[2]+
fpclm$coef[4]*eggcountpcaobj$D2fdPar[3]+
fpclm$coef[5]*eggcountpcaobj$D2fdPar[4]
plot(fpcabeta) 

fpccoefvar = summary(fpclm)$coefficients[,2]^2 # Confidence Intervals
fpcbetavar = fpccoefvar[2]*eggcountpcaobj$D2fdPar[1]^2+
  fpccoefvar[3]*eggcountpcaobj$D2fdPar[2]^2+
  fpccoefvar[4]*eggcountpcaobj$D2fdPar[3]^2+
  fpccoefvar[5]*eggcountpcaobj$D2fdPar[4]^2
lines(fpcabeta+2*sqrt(pcbetavar))
lines(fpcabeta-2*sqrt(fpcbetavar))
```
## Functional penalized principal component regression
```{r Data, message=FALSE, warning=FALSE}
library(fda.usc)
load('E://R Files/Functional Data/Data Sets/fly.Rdata')
train_ind = 1:35
eggcountdata = t(medfly$eggcount)
eggcountfdata = fdata(eggcountdata,names=list("day","eggcount")) # convert data to fdata 
X_train = eggcountfdata[train_ind,]
X_test = eggcountfdata[-train_ind,]
lifespan = medfly$lifetime[train_ind] # Scalar response
lifespan_bar = mean(lifespan)
y_test = medfly$lifetime[-train_ind]

fpcreg = fregre.pc(fdataobj=X_train,y=lifespan,kmax=4,P=c(0,0,1))# Functional penalized PC regression using fpc
fpcreg # R2=0.9435122

lifespan_pre_PPCA = predict(fpcreg,X_test)
osR2_PPCA = osR2(y_test,lifespan_pre_PPCA,lifespan_bar)
print(paste("osR2 =",osR2_PPCA)) # 0.919510231267232

fppcreg = fregre.pls.cv(fdataobj=X_train,y=lifespan,kmax=8,lambda=0:5,P=c(0,0,1)) # Selects the PPLS components with best estimates 
fppcreg$fregre.pls # R2=0.9871092

lifespan_pre_PPCA_cv = predict(fppcreg$fregre.pls,X_test)
osR2_PPCA_cv = osR2(y_test,lifespan_pre_PPCA_cv,lifespan_bar)
print(paste("osR2 =",osR2_PPCA_cv)) # 0.965586093772263
```

# Functional Linear Models (Functional-scale)
```{r Data, message=FALSE, warning=FALSE}
Lcoef = c(0,(2*pi/365)^2,0)
harmaccelLfd = vec2Lfd(Lcoef, c(0,365))
daybasis365 = create.fourier.basis(c(0, 365), 365) # saturated 
lambda = 1e6 # roughness penalty for response variable
tempfdPar =fdPar(daybasis365, harmaccelLfd, lambda) 
tempfd =smooth.basis(day.5, daily$tempav, tempfdPar)$fd # response data Step 1.1
plot(tempfd, col=1, main="Temperature profiles of all cities")
plot(tempfd, col=factor(CanadianWeather$region),
     main="Temperature profiles by region")
coef36 = cbind(tempfd$coef,matrix(0,365,1)) # why we need cbind?
temp36fd = fd(coef36,daybasis365,tempfd$fdnames) # functional response Step 1.2 ??

# Then we create dummy variable for catergory data (dependent)
regions = unique(CanadianWeather$region)
regions # scalar dependent, a list which need to assign dummy value
p = length(regions) + 1 # catergory + constant effect 
regionList = vector("list", p) # initial the dependent parameters (scale), important! 
regionList[[1]] = c(rep(1,35),0) # we have 35 objects, the meaning of 0?
for (j in 2:p) {
  xj = CanadianWeather$region == regions[j-1] # dummy variables
  regionList[[j]] = c(xj,1) # the meaning of 1? Step 2
}

# initial beta
betabasis = create.fourier.basis(c(0, 365), 11) # how to determine the num of betabasis?
betafdPar = fdPar(betabasis) # tranfer to fd type
betaList = vector("list",p)
for (j in 1:p){
  betaList[[j]] = betafdPar # function of t, beta fd  Step 3
}

fRegressList = fRegress(temp36fd, regionList, betaList) # there are three parts
betaestList = fRegressList$betaestlist # beta estimation, function of t, need to interpret
par(mfrow=c(2,2))
for(j in 1:4){
  plot(betaestList[[j]],col=j,main=paste("beta",j),ylim=c(-16,16)) # Plot the Beta Coefficients
  abline(h=0,lty=2)
}
par(mfrow=c(1,1))
regionFit = fRegressList$yhatfd
plot(regionFit, lwd=2, lty=1,xlab="Day", ylab="Temperature",
     ylim=c(-30,20),main="Prediction") # Plot the yhat for different catergory

# Choose the best lambda by using CV
lambda = exp(10:14) 
zmat = cbind(regionList[[1]],regionList[[2]],regionList[[3]],
             regionList[[4]],regionList[[5]]) # dummy variable (dependent) for catergory data
CVmat = matrix(0,length(lambda),35) # initial, the num of 35? should be calculated 
tbetalist = list()
tZlist = list()
for(i in 1:length(lambda)){ # warning: it takes very long time
  for(j in 1:35){
    for(k in 1:5){
      tbetalist[[k]] = fdPar(betabasis,2,lambda[i]) # 2 denote the 2nd derivate
      tZlist[[k]] = zmat[-j,k]
    }
    tres = fRegress(temp36fd[-j],tZlist,tbetalist)
    yhat = 0
    for(k in 1:5){
      yhat = yhat + zmat[j,k]*tres$betaestlist[[k]]$fd
    }
    err = temp36fd[j] - yhat
    CVmat[i,j] = inprod(err,err) # this formula need to understand?
  }
}
save(CVmat,file="CVmat.RData")
CV = apply(CVmat,1,mean)
plot(log(lambda),CV,type='l')
best = which.min(CV)
abline(h=CV[best], v= log(lambda[best]))
grid()

betabasis = create.fourier.basis(c(0, 365), 11)
betafdPar = fdPar(betabasis,2,lambda[best]) # roughness penalty given by CV
betaList = vector("list",p)
for (j in 1:p){
  betaList[[j]] = betafdPar
}

fRegressList = fRegress(temp36fd, regionList, betaList)
betaestList = fRegressList$betaestlist
regionFit = fRegressList$yhatfd
regions = c("Canada", regions) # show the constant beta function, the canada temperature
par(mfrow=c(2,3),cex=1)
for (j in 1:p){
  plot(betaestList[[j]]$fd, lwd=2,col=j,
       xlab="Day",ylim=c(-20,20),
       ylab="", main=regions[j]) # along with the predicted curves for the regions
}
plot(regionFit, lwd=2, lty=1,xlab="Day", ylab="",ylim=c(-30,20),main="Prediction")

# calculate the C.I.
yhatmat = eval.fd(day.5, regionFit[-36]) # so, why we need to add one more col?
resid = daily$tempav - yhatmat # we must have the same type
Sigma = var(t(resid)) 
y2cMap = smooth.basis(day.5, daily$tempav, tempfdPar)$y2cMap # the value of y2cMap need to remember
stderrList = fRegress.stderr(fRegressList, y2cMap, Sigma) # formaula!
save(stderrList,file = "Std.RData")
betastderrlist = stderrList$betastderrlist
par(mfrow=c(2,3),cex=1)
for (j in 1:p){
  beta = betaestList[[j]]$fd
  plot(beta, lwd=2,ylim=c(-20,20),
       xlab="Day",
       ylab="", main=regions[j]) 
  lines(beta + 2*betastderrlist[[j]],lty=2, lwd=1)
  lines(beta - 2*betastderrlist[[j]], lty=2, lwd=1)
  abline(h=0,lty=3)
}

par(mfrow=c(2,3),cex=1)
plotbeta(betaestList,betastderrlist,day.5) # plot all beta coeffecients

```


## We use the refund package to model functional response(functional-functional)
```{r Data, message=FALSE, warning=FALSE}
library(refund)
data(DTI)
DTI1 <- DTI[DTI$visit==1 & complete.cases(DTI),]
# We can apply various preprocessing options to the DTI data
fit1 <- pfr(pasat ~ lf(cca, k=30), data=DTI1)
fit2 <- pfr(pasat ~ lf(cca, k=30, presmooth="fpca.sc",
presmooth.opts=list(nbasis=8, pve=.975)), data=DTI1)
fit3 <- pfr(pasat ~ lf(cca, k=30, presmooth="fpca.face",
presmooth.opts=list(m=3, npc=9)), data=DTI1)
fit4 <- pfr(pasat ~ lf(cca, k=30, presmooth="fpca.ssvd"), data=DTI1)
fit5 <- pfr(pasat ~ lf(cca, k=30, presmooth="bspline",
presmooth.opts=list(nbasis=8)), data=DTI1)
fit6 <- pfr(pasat ~ lf(cca, k=30, presmooth="interpolate"), data=DTI1)
# All models should result in similar fits
fits <- as.data.frame(lapply(1:6, function(i)
get(paste0("fit",i))$fitted.values))
names(fits) <- c("none", "fpca.sc", "fpca.face", "fpca.ssvd", "bspline", "interpolate")
pairs(fits)

# Fit model with linear functional term for CCA
fit.lf <- pfr(pasat ~ lf(cca, k=30, bs="ps"), data=DTI1)
plot(fit.lf, ylab=expression(paste(beta(t))), xlab="t")

# Functional response
set.seed(2121)
data1 <- pffrSim(scenario="ff", n=40)
t <- attr(data1, "yindex")
s <- attr(data1, "xindex")
m1 <- pffr(Y ~ ff(X1, xind=s), yind=t, data=data1)
summary(m1)
plot(m1, pers=TRUE, pages=1)
```
